\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage{merriweather} %% Option 'black' gives heavier bold face 
\usepackage[T1]{fontenc}
\usepackage{xcolor}

\usepackage{dashundergaps} % for dotted underlining

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{0pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\definecolor{awsomeblue}{HTML}{2079C7}
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\color{awsomeblue}
}{}{0em}{}[\color{awsomeblue}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{0pt}}
    }
}

\newcommand{\resumeLineItem}[3]{
    \item[]{
        \textbf{#1}{: #2}\hfill{#3}\vspace{-6pt}
    }
}

\newcommand{\resumeTopItem}[4]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
    \item[]{\small{#4}}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[3]{
    \vspace{0pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}\vspace{0pt}
}

\renewcommand{\labelitemii}{$\circ$} % changes the default bullet to a circle

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Alexander Metzger} & Seattle, WA 98195 \\
    \href{https://sandergi.com}{\underbar{https://sandergi.com}} & \href{mailto:alex@sandergi.com}{\underbar{alex@sandergi.com}} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Koel Labs}{Founder and CEO}{Aug. 2024 -- Present}
\resumeItemListStart
\resumeItem{Raised \$100K in funding}{
    from Mozilla, Next, and partners for computational linguistics research.
}
\resumeItem{First authoring}{
    \underbar{ML} and \underbar{HCI} papers, leading team of 3, training SoTA models with \underbar{PyTorch}.
}
\resumeItem{Python}{
    \underbar{MLOps}, \underbar{Docker}, \underbar{Google Cloud Platform}, \underbar{Azure}, \underbar{AWS}, \underbar{React}, \underbar{NLP}, \underbar{ML for Audio}, \underbar{Streaming}.
}
\resumeItemListEnd

\resumeSubheading{Ubiquitous Computing Lab}{Undergraduate Researcher}{Jun. 2024 -- Present}
\resumeItemListStart
\resumeItem{Co-authored}{
    the SAMIR research paper by leading the data collection effort for 1000s of
    products, inventing the Computer Vision pipeline, designing the UI, and running extensive evaluations.
}
\resumeItem{Python}{
    \underbar{Embedded ML}, \underbar{ML for Sustainability}, \underbar{Computer Vision}, \underbar{Vision Language Models}.
}
\resumeItemListEnd

\resumeSubheading{Seattle Tutoring Partners}{Founder and Research Mentor }{May. 2022 -- Present}
\resumeItemListStart
\resumeItem{Mentoring}{
    research projects for High Schoolers and collaborating with College Students on independent research such as the novel \href{https://github.com/SanderGi/Genus}{\dotuline{PAGE}} algorithm for graph embedding implemented in \underbar{C}.
}
\resumeItem{Developed}{
    \href{https://attendqr.com/}{\dotuline{software}} for 500+ youth musicians and \href{https://github.com/SanderGi/WiFiStrengthTester}{\dotuline{antenna software}} for 8K+ aspiring scientists.
}
\resumeItem{Cascade Enrichment, Technical Lead}{
    managing remote certification and coding curriculum for 30+ tutors; developing and maintaining \href{https://cascadeenrichment.com/elementary-math-assessments}{\dotuline{online assessment platform}} for 100+ students.
}
\resumeItemListEnd

\resumeSubheading{Gooey.AI}{Software Engineer}{Jun. 2023 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Mentored}{
    team of 4 interns through merging 70 pull requests touching 1000s of daily active users.
}
\resumeItem{Deployed}{
    ML solutions to 10M+ farmers across 5+ countries, demoed to 193 world leaders at the UN.
}
\resumeItem{Python}{
    \underbar{MLOps}, \underbar{Kubernetes}, \underbar{Docker}, \underbar{Google Cloud Platform}, \underbar{Django}, \underbar{Azure}, \underbar{OpenAI}, \underbar{Sentry}, \underbar{API design}.
}
\resumeItemListEnd
\vspace{-10pt} % Hacky fix for awkward extra space that randomly appears

\resumeSubheading{University of Washington ICTD Lab}{Undergraduate Researcher}{Sep. 2022 -- May 2024}
\resumeItemListStart
\resumeItem{Shipped}{
    a \href{https://github.com/SanderGi/eKichabi}{\dotuline{USSD server and Android app}} via a digital intervention to connect 10K farmers in Tanzania.
}
\resumeItem{Co-first authored \href{https://sandergi.github.io/images/eKichabi_v2_chi24a.pdf}{\dotuline{eKichabi v2 paper}}}{
    on \href{https://youtu.be/v-1JuQp1ous}{\dotuline{scaling technological interventions in Sub-Saharan Africa}} -- accepted to ACM SIGCHI. Presented \href{https://sandergi.github.io/images/CHANGE_Seminar_Talk_eKichabi_v2.pdf}{\dotuline{a 50 minute talk}} to 40 researchers at the CHANGE Seminar.
}
\resumeItem{Python/Java}{\underbar{Jupyter}, \underbar{Django}, \underbar{MySQL}, \underbar{Redis}, \underbar{HTTP}, \underbar{REST}, \underbar{USSD}/\underbar{Telecom APIs} and \underbar{Android Studio}.}
\resumeItemListEnd

\resumeSubheading{Akvelon}{Software Engineering Intern}{Jun. 2023 -- Aug. 2023}
\resumeItemListStart
\resumeItem{Led}{
    team of 4 to make 200K open-source contributions to 7 Microsoft repos across 27 pull requests.
}
\resumeItem{TypeScript/C++}{
    \underbar{Power BI Custom Visuals}, \underbar{Automated Testing}, \underbar{Embedded Systems}, and \underbar{Azure IOT Hub}.
}
\resumeItemListEnd
\vspace{-10pt} % Hacky fix for awkward extra space that randomly appears

\resumeSubheading{European Environment Agency}{Data Science Intern}{Apr. 2020 -- May. 2022}
\resumeItemListStart
\resumeItem{Authored}{
    3 technical reports and 5 data analysis scripts used internally and by scientists in 40 countries.
}
\resumeItem{Python}{
    \underbar{Pandas}, \underbar{PySpark}, \underbar{Azure ML Studio}, \underbar{Azure Databricks}, and Excel.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeTopItem
{University of Washington}
{3.98 GPA}
{Sep. 2024 -- Jun. 2026}{
    Masters in Computer Science, UWSO First Violin Section, DubHacks Next Project Track
}
\resumeTopItem
{University of Washington}
{3.87 GPA, 3.96 in CS}
{Sep. 2022 -- Jun. 2025}{
    Bachelor's in Computer Science and Mathematics, Design Build Fly CS Lead, Accelerated Honors Math
}
\resumeSubHeadingListEnd

% %-----------PROJECTS-----------------
% \section{Projects}
% \resumeSubHeadingListStart
% \resumeTopItem{\href{URL}{\dotuline{URL TEXT}}}{KIND}{Sep. 2024 -- Present}{
%     DESCRIPTION
% }
% \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeLineItem{Languages}{JavaScript, TypeScript, Python, Java, C, C++, C\#, SQL}{6+ years}
\resumeLineItem{Tech}{Cloud (GCP, Azure, AWS), REST, PyTorch, Auto Testing, React, Docker, Unix, Git}{3+ years}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
