\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{merriweather} %% Option 'black' gives heavier bold face 
\usepackage[T1]{fontenc}
\usepackage{xcolor}

\usepackage{dashundergaps} % for dotted underlining

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{0pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\definecolor{awsomeblue}{HTML}{2079C7}
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\color{awsomeblue}
}{}{0em}{}[\color{awsomeblue}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{#2 \vspace{-2pt}}\strut
    }
}

\newcommand{\resumeLineItem}[3]{
    \item[]{
        \textbf{#1}{: #2}\hfill{#3}\vspace{-6pt}
    }
}

\newcommand{\resumeTopItem}[4]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
    \item[]{\small{#4}}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[3]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}\vspace{0pt}
}

\usepackage{colortbl}
\definecolor{Gray}{gray}{0.85}
\newcommand{\resumeSubheadingStrong}[3]{
    \vspace{-1pt}\item[]
    \begingroup\setlength{\fboxsep}{1pt}
    \hspace{-5pt}\colorbox{lightgray}{
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \vspace{-2pt}\textbf{#1} -- \textit{#2} & #3 \\
        \end{tabular*}
    }\endgroup\vspace{-15pt}\vspace{0pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-1pt}\item[]
    \textbf{#1} #2
    \vspace{-2pt}
}

\renewcommand{\labelitemii}{$\circ$} % changes the default bullet to a circle

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Alexander Metzger} & Seattle, WA 98195 \\
    \href{https://sandergi.com}{\underbar{https://sandergi.com}} & \href{mailto:alex@sandergi.com}{\underbar{alex@sandergi.com}} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeTopItem
{University of Washington}
{3.87 GPA}
{09/22 -- 06/26}{
    BS in Mathematics and CS, Accelerated Honors Math, Math Departmental Honors, UWSO First Violin Section
}
\resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubheadingStrong{University of Washington}{Independent, advised by: Dr. Stefan Steinerberger}{Sep. 2024 -- Present}
\resumeSubSubheading{Practical algorithm for graph embedding.}{Graph Theory, Algorithms, Combinatorics. \href{https://github.com/SanderGi/Genus}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Design a specialized algorithm optimized for embedding cage graphs.}
\resumeItemListStart
\resumeItem{Invented and Implemented}{
    algorithm in \underbar{C} with visualization and verification in \underbar{SageMath}.
}
\resumeItem{Co-authored}{
    the research paper [P1] with fellow Mathematics major Austin Ulrigg.
}
\resumeItemListEnd

\resumeSubheadingStrong{Ubiquitous Computing Lab}{Advisor: Dr. Shwetak Patel}{Jun. 2024 -- Present}
\resumeSubSubheading{Mathematical models for urban sound localization and battery-free autonomous flight control.}{}
\resumeSubSubheading{Goal:}{Low-cost, low-power environmental monitoring to predict disasters like wildfires.}
\resumeSubSubheading{Statistical lifecycle assessment models for consumer and industrial electronics.}{}
\resumeSubSubheading{Goal:}{Democratize access to environmental impact estimates and empower sustainable consumption.}
\resumeItemListStart
\resumeItem{Co-authored}{ the ACM MobiSys 2025 paper by designing statistical and \underbar{Computer Vision} models.}
\resumeItemListEnd

\resumeSubheadingStrong{ICTD Lab}{Advisor: Dr. Richard Anderson}{Sep. 2022 -- May 2024}
\resumeSubSubheading{Digital phone directory for subsistence farmers in rural Tanzania.}{\href{https://github.com/SanderGi/eKichabi}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Study the economic impacts of digital agricultural information systems in Sub-Saharan Africa.}
\resumeItemListStart
\resumeItem{Led}{
    UW SWE team in multi-million-USD, multi-year collaboration with Cornell, EDI Global, and IRDP.
}
\resumeItem{Presented}{
    live [T1,2] and video talks [T3] about the 10K farmers we helped across 5 districts in Tanzania.  
}
\resumeItem{Co-first-authored}{
    the paper [P2] accepted to ACM SIGCHI 2024 and led statistical analysis.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Favorite Publications}
\resumeSubHeadingListStart
\resumeTopItem{[P2]}{\href{https://doi.org/10.1145/3613904.3642099}{\dotuline{Peer Reviewed and Published}}, Co-first}{\underbar{Economics}, \underbar{ICTD}}{
    Ananditha Raghunath, \textbf{Alexander Metzger}, Hans Easton, XunMei Liu, Fanchong Wang, Yunqi Wang, Yunwei Zhao, Hosea Mpogole, and Richard Anderson. 2024. eKichabi v2: Designing and Scaling a Dual-Platform Agricultural Technology in Rural Tanzania. In Proceedings of the CHI Conference on Human Factors in Computing Systems (CHI '24), May 11-16, 2024, Honolulu, HI, USA. ACM, New York, NY, USA, 16 pages.
}
\resumeTopItem{[P1]}{\href{https://arxiv.org/abs/2411.07347}{\dotuline{Submitted to Discrete Mathematics}}, Co-first}{\underbar{Algorithms}, \underbar{Graph Combinatorics}}{
    \textbf{Alexander Metzger} and Austin Ulrigg. An Efficient Genus Algorithm Based on Graph Rotations.
}
\resumeSubHeadingListEnd

%-----------TALKS-----------------
\section{Talks}
\resumeSubHeadingListStart
\resumeTopItem{[T4]}{\href{https://www.washington.edu/urs/visitors/}{\dotuline{Graph Algorithms, Discrete Combinatorial Optimization, and Genus}}}{May 2025}{
    Universifty of Washington Undergraduate Research Symposium, Seattle, WA
}
\resumeTopItem{[T4]}{\href{https://docs.google.com/presentation/d/16tZGX8pRINhTTnhDZHCynEDKyfHl0I9tVnjHukLFnuM/mobilepresent?slide=id.p}{\dotuline{Computational Linguistics for Machine Aided Pronunciation Learning}}}{Oct. 2024}{
    University of Washington Computational Linguistics Group, Seattle, WA
}
\resumeTopItem{[T3\&2]}{\href{https://parachidub.wpcomstaging.com/}{\dotuline{eKichabi v2: Designing and Scaling a Dual Platform Technology in Rural Tanzania}}}{May 2024}{
    ACM SIGCHI Video Presentation, Remote AND Design Use Build's Para.chi Event, Seattle, WA
}
\resumeTopItem{[T1]}{\href{https://sandergi.com/images/CHANGE_Seminar_Talk_eKichabi_v2.pdf}{\dotuline{Designing and Deploying Digital Information Systems in Sub-Saharan Africa}}}{Oct. 2023}{
    University of Washington CHANGE Seminar, Seattle, WA
}
\resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading{Koel Labs}{Founder and CEO}{Aug. 2024 -- Present}
\resumeItemListStart
\resumeItem{Raised \$100K in funding}{
    from Microsoft and partners [H3,5,6] for computational linguistics research.
}
\resumeItem{First authoring}{
    machine learning papers and talks [T4] on novel mathematical modeling of speech.
}
\resumeItemListEnd

\resumeSubheading{Gooey.AI}{Software Engineer}{Jun. 2023 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Mentored}{
    team of 4 interns through merging 70 pull requests touching 1000s of daily active users.
}
\resumeItem{Deployed}{
    \underbar{ML} solutions to 10M+ farmers across 5+ countries, demoed to 193 world leaders at the UN.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
\resumeSubHeadingListStart

\resumeSubheading{Seattle Tutoring Partners}{Founder and Research Mentor}{May 2022 -- Present}
\resumeItemListStart
\resumeItem{Mentoring}{ K-12 students through Calculus, Stats, Algebra, and \href{https://scat6-web.web.app}{\dotuline{internationaly recognized research}}.}
\resumeItem{Serving}{
    \href{https://attendqr.com/}{\dotuline{500+ youth musicians}} and \href{https://github.com/SanderGi/WiFiStrengthTester}{\dotuline{10K+ aspiring scientists}} through custom mathematical software.
}
\resumeItemListEnd

\resumeSubheading{Cascade Enrichment}{Technical Lead}{Sep. 2022 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Managed}{
    math curriculum for 30+ tutors and online math assessment platform for 100+ students.
}
\resumeItemListEnd

\resumeSubheading{Design Build Fly}{Lead Computer Scientist}{Sep. 2023 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Coordinated}{
    aerodynamic modeling and optimization team of 30; secured international 3rd place [H2].
}
\resumeItemListEnd

\resumeSubheading{Akvelon, Inc.}{Intern Software Development Manager}{Jun. 2023 -- Aug. 2023}
\resumeItemListStart
\resumeItem{Led}{
    team of 4 to make open-source accessibility contributions to 7 Microsoft data analysis tools [H1].
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%--------HONORS AND DISTINCTIONS------------
\section{Honors and Distinctions}
\resumeSubHeadingListStart
\resumeLineItem{[H6] Meta+8VC Next Llama Stack Hackathon}{1st Place, \$1K Prize}{2025}
\resumeLineItem{[H5] Microsoft Imagine Cup}{Semifinalist, \$5K cloud credits}{2025}
\resumeLineItem{[H4] CRA Outstanding Undergraduate Researcher Award}{Honorable Mention}{2025}
\resumeLineItem{[H3] Mozilla Builders Accelerator}{\$39K research grant, \$35K cloud credits}{2024}
\resumeLineItem{[H2] Design Build Fly Annual Competition}{International 3rd Place}{2024}
\resumeLineItem{[H1] Akvelon Mentor's Choice}{Outstanding Leadership}{2023}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Math Skills}
\resumeSubHeadingListStart
\resumeLineItem{Computational Tools}{Mathematica, SageMath, Matlab, PyTorch, C/C++}{3+ years}
\resumeLineItem{Classes}{Abstract+Linear Algebra, Combinatorics, Probability, Numerical Analysis, Stats}{3+ years}
\resumeLineItem{Applied}{Aerodynamics, Antenna Design, Machine Learning, Economics, Teaching}{3+ years}
\resumeLineItem{Research}{Study Design, Clinical Trials, Paper Writing, Grant Applications, Presentation}{3+ years}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
