\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{pgfplots}
\pgfplotsset{compat = newest}
\usepackage{graphicx}
\usepackage[shortlabels]{enumitem}
\usepackage[stable]{footmisc} % allow footnotes in section titles
\addtolength{\skip\footins}{2pc plus 5pt} % give footnotes some breathing room
\usepackage[T1]{fontenc} % fix underscore from \jobname
\usepackage{float}
\usepackage{subcaption} % subfigures

% Laplace Operator
\usepackage{mathtools}
\DeclarePairedDelimiterXPP\Laplace[1]{\operatorname{\mathcal{L}}}{\{}{\}}{}{#1}
\DeclarePairedDelimiterXPP\LaplaceInv[1]{\operatorname{\mathcal{L}^{-1}}}{\{}{\}}{}{#1}

% Derivatives
\newcommand*{\Partial}[2]{\frac{\partial #1}{\partial #2}}
\newcommand*{\Deriv}[2]{\frac{d #1}{d #2}}

% augmented coefficient matrix
\newenvironment{amatrix}[1]{%
    \left(\begin{array}{@{}*{#1}{c}|c@{}}
}{%
    \end{array}\right)
}

% rules 
\newcommand*{\vertbar}{\rule[-1ex]{0.5pt}{2.5ex}}
\newcommand*{\horzbar}{\rule[.5ex]{2.5ex}{0.5pt}}

% common sets
\newcommand*{\R}{\mathbb{R}}
\newcommand*{\C}{\mathbb{C}}
\newcommand*{\Z}{\mathbb{Z}}
\newcommand*{\N}{\mathbb{N}}
\newcommand*{\Q}{\mathbb{Q}}
\newcommand*{\D}{\mathbb{D}}

% inner products
\newcommand*{\Inner}[1]{\langle #1 \rangle}

% formatting
\newcommand*{\parspace}{\vspace{1em} \\}

% vectors
\newcommand*{\vx}{\mathbf{x}}
\newcommand*{\vy}{\mathbf{y}}
\newcommand*{\vz}{\mathbf{z}}
\newcommand*{\va}{\mathbf{a}}
\newcommand*{\vb}{\mathbf{b}}
\newcommand*{\vc}{\mathbf{c}}
\newcommand*{\vF}{\mathbf{F}}
\newcommand*{\vG}{\mathbf{G}}
\newcommand*{\vH}{\mathbf{H}}
\newcommand*{\vn}{\mathbf{n}}
\newcommand*{\vm}{\mathbf{m}}
\newcommand*{\vf}{\mathbf{f}}
\newcommand*{\vg}{\mathbf{g}}
\newcommand*{\vh}{\mathbf{h}}
\newcommand*{\vi}{{\mathbf{\hat{\textnormal{\bfseries\i}}}}}
\newcommand*{\vj}{{\mathbf{\hat{\textnormal{\bfseries\j}}}}}
\newcommand*{\vk}{{\mathbf{\hat{\textnormal{\bfseries k}}}}}
\newcommand*{\vzero}{\mathbf{0}}

\usepackage{xstring}
\title{\StrSubstitute{\jobname}{"}{}}
\author{Alexander Metzger}
\date{}

\begin{document}

\maketitle

I started playing the violin when I was four and a half with the Danish Suzuki
Institute. It has been a constant comfort, even as I was uprooted and moved to the US
seven years ago, shaping my resilience and initiative. The support I received from teachers
and friendships I made with peers, kindled my high school interest in mentoring and
motivated me to teach music to elementary schools with Seattle Music Partners (SMP).
\\\\
\indent When SMP was struck down by COVID, I carried on the torch and founded my own
tutoring company (creatively named Seattle Tutoring Partners) to keep teaching music. I
also started teaching coding and connecting mentors with students. Going into college, I
had created the Tech Leadership position at Cascade Enrichment to write accessible
assessment software for students and empower tutors to teach coding remotely through a
curated curriculum and remote learning certification program.
\\\\
\indent Now in college, I continue to mentor students in academic subjects, music, research
projects, and science olympiad events. Violin is an active part of my life in the UW
Symphony Orchestra and continues to teach me how crucial teamwork and discipline are,
both in and out of music. This propensity to discipline and teamwork compliments my
drive to pursue opportunities that combine technical growth with leadership.
\\\\
\indent As Lead Computer Scientist for Design Build Fly, a student organization for
RC-plane building enthusiasts, my co-leads and I led our team to secure the annual bronze
medal. I'm putting the experience with sensor data and aircraft optimization to direct use
in my research with the UbiComp Lab. As a math discord member, I took action on an
unsolved genus problem which led to research with Dr. Stefan Steinerberger. Motivated by
these positive experiences in my communities, I seek to positively impact marginalized
communities through my research.

\end{document}
