\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{merriweather} %% Option 'black' gives heavier bold face 
\usepackage[T1]{fontenc}
\usepackage{xcolor}

\usepackage{dashundergaps} % for dotted underlining

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{0pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\definecolor{awsomeblue}{HTML}{2079C7}
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\color{awsomeblue}
}{}{0em}{}[\color{awsomeblue}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{#2 \vspace{-2pt}}
    }
}

\newcommand{\resumeLineItem}[3]{
    \item[]{
        \textbf{#1}{: #2}\hfill{#3}\vspace{-6pt}
    }
}

\newcommand{\resumeTopItem}[4]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
    \item[]{\small{#4}}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[3]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}\vspace{0pt}
}

\usepackage{colortbl}
\definecolor{Gray}{gray}{0.85}
\newcommand{\resumeSubheadingStrong}[3]{
    \vspace{-1pt}\item[]
    \begingroup\setlength{\fboxsep}{1pt}
    \hspace{-5pt}\colorbox{lightgray}{
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \vspace{-2pt}\textbf{#1} -- \textit{#2} & #3 \\
        \end{tabular*}
    }\endgroup\vspace{-15pt}\vspace{0pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-1pt}\item[]
    \textbf{#1} #2
    \vspace{-2pt}
}

\renewcommand{\labelitemii}{$\circ$} % changes the default bullet to a circle

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Alexander Metzger} & Seattle, WA 98195 \\
    \href{https://sandergi.com}{\underbar{https://sandergi.com}} & \href{mailto:alex@sandergi.com}{\underbar{alex@sandergi.com}} \\
\end{tabular*}

%----------Summary-----------------
\vspace{0.2cm}
My research aims to bridge gaps in information access for underserved
languages and communities through a combination of algorithm design,
machine learning, and edge device technology.

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeTopItem
{University of Washington}
{3.85 GPA, 3.97 in CS}
{09/22 -- 06/26}{
    Joint BS/MS Computer Science and BS Mathematics, Graduate Compilers \& Cloud Security Teaching Assistant, UWSO First Violin, Accelerated Honors Math, Guest Lecturer [T7, T8, T9], NeurIPS reviewer, COM$^2$ Mentor.
}
\resumeSubHeadingListEnd

%--------AWARDS AND FUNDING------------
\section{Awards}
\resumeSubHeadingListStart
\resumeLineItem{[H3] CRA Outstanding Undergraduate Researcher Award}{\href{https://news.cs.washington.edu/2025/01/31/allen-school-undergraduates-receive-national-recognition-for-research-contributions/}{\dotuline{Honorable Mention}}}{2025}
\resumeLineItem{[H2] Departmental Honors and Dean's List}{Annual and Quarterly}{2022-2025}
\resumeLineItem{[H1] Akvelon Mentor's Choice}{Outstanding Leadership}{2023}
\resumeSubHeadingListEnd

\section{Funding}
\resumeSubHeadingListStart
\resumeTopItem{[F6] Mozilla Builders Accelerator}{\$39K research grant, \$35K cloud credits}{2024\hspace{-3pt}}{
    Youngest out of 14 founders and researchers selected from \href{https://blog.mozilla.org/en/mozilla/14-ai-projects-to-watch-mozillas-first-builders-accelerator-cohort-kicks-off/}{\dotuline{44 countries \& 100s of applicants}}. Featured on the \href{https://stackoverflow.blog/2025/07/11/how-your-favorite-movie-is-changing-language-learning-technology/}{\dotuline{Stack Overflow}} podcast with more than 2 million viewers. Praised as ``most promising'' by \href{https://siliconangle.com/2024/09/23/mozilla-kicks-off-builders-accelerator-program-local-ai-startups/}{\dotuline{Silicon}} \& \href{https://pulse2.com/mozilla-reveals-funding-for-14-ai-projects-as-part-of-builders-accelerator-program/}{\dotuline{Pulse}}.}
\resumeLineItem{[F5] Microsoft Imagine Cup}{Semifinalist, \$5K cloud credits}{2025}
\resumeLineItem{[F4] Facebook AI for Health Challenge}{1st Place, \$1K Prize}{2025}
\resumeLineItem{[F3] Google Research}{Special Google TPU Research Cloud Access}{2025}
\resumeLineItem{[F2] Nvidia Inception}{Accepted Startup Founder, GPUs}{2025}
\resumeLineItem{[F1] Clean Energy Institute}{TARs Research Grant}{2025}
\resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubheadingStrong{Ubiquitous Computing Lab}{Advisor: Dr. Shwetak Patel}{Jun. 2024 -- Present}
\resumeSubSubheading{Battery-Free DL on MCUs via Agentic Model and System Optimization.}{Embedded ML. \href{https://github.com/SanderGi/YADES}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Automatically adapt Deep Learning models to ultra-low-power hardware/microcontrollers.}
\resumeItemListStart
\resumeItem{Developed}{
    a novel model compression framework for hardware constraints in MCU accelerators.
}
\resumeItem{Co-first-authored}{
    paper submitted to ACM IMWUT [P6] analyzing applications including animal monitoring to prevent crop destruction, and wearables to assess linguistic development in toddlers.
}
\resumeItem{Created}{
    SoTA speech2ipa models that retain top performance with 600x smaller memory footprint.
}
\resumeItem{Learned}{
    from the amazing Zhihan Zhang (best advisor at the University of Washington).
}
\resumeItemListEnd

\resumeSubheadingStrong{CS 4 The Environment}{Advisor: Dr. Vikram Iyer}{Jun. 2024 -- Present}
\resumeSubSubheading{Multi-modal automated lifecycle assessments of consumer electronics.}{ML for sustainability. \href{https://github.com/iamZhihanZhang/Living-Sustainability}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Democratize access to environmental impact estimates and empower sustainable consumption.}
\resumeItemListStart
\resumeItem{Co-authored}{
    study design and research papers [P2, P4] and presented the work at top events [T10, T13].
}
\resumeItem{Industry adoption}{
    of our work by Google and Amazon as well as a publicly accessible Chrome Extension.
}
\resumeItem{Designed}{
    the multi-modal pipeline, enabling agents to consolidate information from many fragmented sources and departments (online tear downs, FCC records, environmental reports, company data).
}
\resumeItemListEnd

\resumeSubheadingStrong{ICTD Lab}{Advisor: Dr. Richard Anderson}{Sep. 2022 -- May 2024}
\resumeSubSubheading{eKichabi v2: Digital phone directory for subsistence farmers in rural Tanzania.}{ICTD. \href{https://github.com/SanderGi/eKichabi}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Study the economic impacts of digital agricultural information systems in Sub-Saharan Africa.}
\resumeItemListStart
\resumeItem{Co-first-authored}{
    the paper [P5] accepted to ACM SIGCHI 2024. Presented talks [T7, T12].
}
\resumeItem{Led}{
    team of 4 developers for the USSD server and later also the Android App optimizing latency by 40\%.
}
\resumeItem{Designed}{
    a binary protocol reducing data costs by 70\%, making the platform accessible to 10K farmers.
}
\resumeItemListEnd

\resumeSubheadingStrong{UBC NLP Group}{Advisor: Dr. Jian Zhu}{Sep. 2024 -- Present}
\resumeSubSubheading{Transcribing in Context: Temporal Trends in ASR Biases.}{Inclusive Speech Technology. \href{https://nlp.cs.ubc.ca/}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Re-evaluate the claim that speech models are becomming more universal in context of dialects.}
\resumeItemListStart
\resumeItem{First-authoring}{
    the ACM FAccT submission, mentoring an undergrad and a high school student.
}
\resumeItem{First}{
    comprehensive evaluation of ASR model regressions over time for minority speaker profiles.
}
\resumeItem{Assembled}{
    a diverse research team from Korea, England, Denmark, Japan, India, Canada, and the US.
}
\resumeItem{Quantifying}{
    real world impact on immigration processes, job acquisition, and information access.
}
\resumeItemListEnd

\resumeSubheadingStrong{ChangeLing Lab}{Advisor: Dr. David R. Mortensen}{Sep. 2025 -- Present}
\resumeSubSubheading{PhoneBench: Towards Universal Phoneme Recognition.}{Computational Linguistics. \href{https://changelinglab.github.io/people/}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Device an inclusive benchmark for phoneme recognition and plan for a universal model.}
\resumeItemListStart
\resumeItem{Established}{
    the \href{https://huggingface.co/spaces/KoelLabs/IPA-Transcription-EN}{\dotuline{current standard phoneme recognition leaderboard}} and trained the \href{https://huggingface.co/KoelLabs/xlsr-english-01}{\dotuline{top model}}.
}
\resumeItem{Mentoring}{
    a high school student and collaborating with the PhD/MS students at the lab on a unique method to evaluate phonetic model bias against underserved dialects through representation learning.
}
\resumeItem{Pioneering}{
    a new approach to universal phoneme transcription using in-context learning.
}
\resumeItemListEnd

\resumeSubheadingStrong{University of Washington}{Advisor: Dr. Stefan Steinerberger}{Sep. 2024 -- Present}
\resumeSubSubheading{Practical algorithms for graph embedding.}{Graph Theory, Algorithms, Combinatorics. \href{https://github.com/SanderGi/Genus}{\dotuline{Link}.}}
\resumeSubSubheading{Goal:}{Compute the genus of the previously intractable (3, 12)-cage graph (turns out it is 17).}
\resumeItemListStart
\resumeItem{Invented and implemented}{
    SoTA algorithm in C with visualization and verification in Python.
}
\resumeItem{Started as independent research}{
    and then reached out to Professor Steinerberger and Brinkmann.
}
\resumeItem{Co-first authored}{
    paper submitted to Discrete Mathematics, published thesis, and gave talks [T4, T6].
}
\resumeItem{Taking}{
    a novel approach to extend prior work on shortcuts to characterize higher genus obstructions.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
\resumeSubHeadingListStart
\resumeTopItem{[P6]}{Submitted to ACM IMWUT}{\underbar{Embedded ML}, \underbar{Wearables}, \underbar{Agents}}{
    \textbf{Alexander Metzger}*, Jiuyang Lyu*, Chun-Cheng Chang, Jiayi Shao, Emmanuel Azuh, Yujia Liu, Zachary Englhardt, Ethan Schwartz, Devin Mackenzie, Gregory D. Abowd, Edward Wang, Tingyu Cheng, Kurtis Heimerl, Shwetak Patel, Vikram Iyer, Zhihan Zhang. Battery-Free Deep Learning on MCUs via Agentic Model and System Co-Optimization.
}
\resumeTopItem{[P5]}{\href{https://doi.org/10.1145/3613904.3642099}{\dotuline{ACM SIGCHI}}}{\underbar{HCI}, \underbar{ICTD}}{
    Ananditha Raghunath*, \textbf{Alexander Metzger}*, Hans Easton, XunMei Liu, Fanchong Wang, Yunqi Wang, Yunwei Zhao, Hosea Mpogole, and Richard Anderson. 2024. eKichabi v2: Designing and Scaling a Dual-Platform Agricultural Technology in Rural Tanzania.
}
\resumeTopItem{[P4]}{\href{https://dl.acm.org/doi/10.1145/3749488}{\dotuline{ACM IMWUT}}}{\underbar{ML for Sustainability}, \underbar{CV}, \underbar{HCI}}{
    Zhihan Zhang, Puvarin Thavikulwat, \textbf{Alexander Metzger}, Yuxuan Mei, Felix Hähnlein, Zachary Englhardt, Gregory D. Abowd, Shwetak Patel, Adriana Schulz, Tingyu Cheng, and Vikram Iyer. 2025. Living Sustainability: In-Context Interactive Environmental Impact Communication.
}
\resumeTopItem{[P3]}{\href{https://arxiv.org/abs/2411.07347}{\dotuline{Pre-print, submitted to Discrete Mathematics}}}{\underbar{Algorithms}, \underbar{Graph Combinatorics}}{
    \textbf{Alexander Metzger}* and Austin Ulrigg*. An Efficient Genus Algorithm Based on Graph Rotations.
}
\resumeTopItem{[P2]}{\href{https://arxiv.org/abs/2507.17012}{\dotuline{Pre-print, submitted to Nature Electronics}}}{\underbar{ML for Sustainability}, \underbar{CV}, \underbar{Agents}}{
    Zhihan Zhang, \textbf{Alexander Metzger}, Yuxuan Mei, Felix Hähnlein, Zachary Englhardt, Tingyu Cheng, Gregory D. Abowd, Shwetak Patel, Adriana Schulz, Vikram Iyer. Towards Autonomous Sustainability Assessment via Multimodal AI Agents.
}
\resumeTopItem{[P1]}{\href{https://hdl.handle.net/1773/53829}{\dotuline{University of Washington Student Research Paper}}}{\underbar{Topology}, \underbar{Graph Theory}, \underbar{Algorithms}}{
    \textbf{Alexander Metzger}. A Practical Algorithmic Approach to Graph Embedding. University of Washington. Department of Mathematics. Honors Thesis. https://hdl.handle.net/1773/53829.
}
% \resumeTopItem{[P1]}{Pre-print, First}{\underbar{HCI}, \underbar{CV}, \underbar{Medical ML}}{
%     \textbf{Alexander Metzger} and Aureole. Digitized Concussion Tests Using Computer Vision and Speech Recognition.
% }
\resumeSubHeadingListEnd

%-----------TALKS-----------------
\section{Talks}
\resumeSubHeadingListStart
\resumeTopItem{[T13]}{\href{https://docs.google.com/presentation/d/1XNRk8qb2RPiSYrVpxZaxItbfVP-UmISv/edit?usp=sharing\&ouid=110368631524695946265\&rtpof=true\&sd=true}{\dotuline{In-Context
            Interactive Environmental Impact Communication}}}{Oct. 2025}{ DUB
    Research Day, Seattle, WA [100s of attendees, only undergrad of 8
            invited speakers] }

\resumeTopItem{[T12]}{\href{https://parachidub.wpcomstaging.com/}{\dotuline{eKichabi v2: Designing and Scaling a Dual Platform Technology in Rural Tanzania}}}{May 2024}{
    DUB Para.chi Event, Seattle, WA [100s of attendees, youngest invited speaker]
}

\resumeTopItem{[T11]}{\href{https://www.interspeech2025.org/home}{\dotuline{Deploying Speech Technology at Scale}}}{Aug. 2025}{
    Interspeech Conference, Rotterdam, Netherlands [2K attendees, 1 of 4 speakers invited for the science slam]
}

\resumeTopItem{[T10]}{\href{https://docs.google.com/presentation/d/1XNRk8qb2RPiSYrVpxZaxItbfVP-UmISv/edit?usp=sharing\&ouid=110368631524695946265\&rtpof=true\&sd=true}{\dotuline{In-Context Interactive Environmental Impact Communication}}}{Oct. 2025}{
    Paul G. Allen's Annual Research Showcase, Seattle, WA [100s of attendees, 3 posters and a talk]
}

\resumeTopItem{[T9]}{\href{https://sandergi.com/images/MAX78000_DEMO.pdf}{\dotuline{Embedded ML - Computer Vision Demo}}}{Oct. 2025}{
    University of Washington Embedded Systems Capstone Guest Talk, Seattle, WA [20 students]
}

\resumeTopItem{[T8]}{\href{https://docs.google.com/presentation/d/16tZGX8pRINhTTnhDZHCynEDKyfHl0I9tVnjHukLFnuM/mobilepresent?slide=id.p}{\dotuline{Computational Linguistics for Machine Aided Pronunciation Learning}}}{Oct. 2024}{
    University of Washington Computational Linguistics Group  Guest Talk, Seattle, WA [30 PhD attendees]
}

\resumeTopItem{[T7]}{\href{https://sandergi.com/images/CHANGE_Seminar_Talk_eKichabi_v2.pdf}{\dotuline{Designing and Deploying Digital Information Systems in Sub-Saharan Africa}}}{Oct. 2023}{
    University of Washington CHANGE Seminar Guest Talk, Seattle, WA [40 PhD attendees]
}

\resumeTopItem{[T6]}{\href{https://docs.google.com/presentation/d/1Giw_u8XKrby_i51ffmLsIflefSI6qQem0FtMYbfchZs/edit?usp=sharing}{\dotuline{Graph Algorithms and Optimization}}}{Nov. 2025}{
    Northwest Undergraduate Mathematics Symposium, Bothell, WA [30 attendees]
}

\resumeTopItem{[T4\&T5]}{\href{https://docs.google.com/presentation/d/1Giw_u8XKrby_i51ffmLsIflefSI6qQem0FtMYbfchZs/edit?usp=sharing}{\dotuline{Graph Embedding and Genus}} | \href{https://docs.google.com/presentation/d/1i_Cgw6-gkC61TXUSUXWIr0OdXsFOMHFp1-PsEdg3Rvk/edit?usp=sharing}{\dotuline{Speech Technology Built For Everyone, Everwhere}}}{May. 2025}{
    University of Washington Research Symposium, Seattle, WA [60 attendees]
}

\resumeTopItem{[T2\&T3]}{\href{https://www.youtube.com/watch?v=oWEe9op0bb0}{\dotuline{The Future of Language Learning}}}{Sep. \& Dec. 2024}{
    Mozilla Builders, New York, NY | Mozilla Builders, San Francisco, CA [500 attendees]
}

\resumeTopItem{[T1]}{\href{https://www.youtube.com/watch?v=oWEe9op0bb0}{\dotuline{Building Inclusive Speech Technology}}}{Apr. 2025}{
    DubHacks Next Demo Day, Seattle, WA [100 attendees]
}
\resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading{Koel Labs}{Founder and CEO}{Aug. 2024 -- Present}
\resumeItemListStart
\resumeItem{Raised \$100K in funding}{
    (Mozilla, Microsoft, Google, Nvidia) for computational linguistics research.
}
\resumeItem{Trained}{
    SoTA NLP models, cutting streaming latency by 60\% and doubling accuracy.
}
\resumeItem{Managed}{
    open-source team of 4 engineers and 6 researchers from CMU, UToronto, UT Austin, and UBC.
}
\resumeItem{Established}{
    strategic partnerships and research collaborations with 5 companies and 5 institutions.
}
\resumeItemListEnd

\resumeSubheading{Gooey.AI}{Software Engineer}{Jun. 2023 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Led}{
    client communication and 4-member intern team, merging 70+ PRs across production ML pipelines.
}
\resumeItem{Deployed}{
    \underbar{ML} solutions to 10M+ farmers across 5+ countries, demoed to 193 world leaders at the UN.
}
\resumeItemListEnd

\resumeSubheading{Akvelon, Inc.}{Software Development Intern}{Jun. 2023 -- Aug. 2023}
\resumeItemListStart
\resumeItem{Led}{
    team of 4 to make 200K open-source contributions to 7 Microsoft repos across 27 pull requests.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
\resumeSubHeadingListStart

\resumeSubheading{Seattle Tutoring Partners}{Founder and Research Mentor}{May 2022 -- Present}
\resumeItemListStart
\resumeItem{Mentoring}{ research projects for High Schoolers, and collaborating on \href{https://scat6-web.web.app}{\dotuline{internationaly recognized projects}}.}
\resumeItem{Developed}{
    \href{https://attendqr.com/}{\dotuline{software}} for 500+ youth musicians and \href{https://github.com/SanderGi/WiFiStrengthTester}{\dotuline{antenna software}} for 10K+ aspiring scientists.
}
\resumeItemListEnd

\resumeSubheading{Cascade Enrichment}{Technical Lead}{Sep. 2022 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Managing}{
    certification and curriculum for 30+ tutors; developed online platform for 100+ students.
}
\resumeItemListEnd

\resumeSubheading{Design Build Fly}{Lead Computer Scientist}{Sep. 2023 -- Sep. 2024}
\resumeItemListStart
\resumeItem{Coordinated}{
    optimization algorithms and data analysis for 30 engineers; placing 3rd nationally.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Courses-----------------
\section{Relevant Coursework}
\small
\resumeSubHeadingListStart
\item[] \textbf{HCI:} Capstone Software Design to Empower Underserved Populations, Software Design and Implementation, Social Networks, Photography, Robotics Colloquium, Computer Science Colloquium
\item[] \textbf{Systems:} Compilers, Operating Systems, Computer Communication Networks, Distributed Systems, Systems Programming, Hardware/Software Interface,
Computer Systems Architecture, Computer Graphics, Concurrency/Parrallelism and Rust, Digital Design, Coursera Nand To Tetris
\item[] \textbf{ML:} Capstone Natural Language Processing, Computational Biology, Probabilistic Robotics, Probability and Statistics, Reinforcement Learning, Machine Learning by Andrew Ng
\item[] \textbf{Theory:} Theory of Computation, Algorithms, Modern Algorithms,
Data Structures and Parallelism, Numerical Analysis, Combinatorics, Quantum Information/Computation, Cryptography, Modern Algebra and Coding Theory, Databases, Linear Algebra, Differential Equations, Vector Calculus
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
