\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{merriweather} %% Option 'black' gives heavier bold face 
\usepackage[T1]{fontenc}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{0pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\definecolor{awsomeblue}{HTML}{2079C7}
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\color{awsomeblue}
}{}{0em}{}[\color{awsomeblue}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeLineItem}[3]{
    \item[]{
        \textbf{#1}{: #2}\hfill{#3}\vspace{-6pt}
    }
}

\newcommand{\resumeTopItem}[4]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
    \item[]{\small{#4}}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[3]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}\vspace{0pt}
}

\renewcommand{\labelitemii}{$\circ$} % changes the default bullet to a circle

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Alexander Metzger} & Seattle, WA 98195 \\
    \href{https://sandergi.github.io/}{\underbar{https://sandergi.github.io/}} & \href{mailto:alexander.le@outlook.dk}{\underbar{alexander.le@outlook.dk}} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Gooey.AI}{Machine Learning Intern}{Jun. 2023 -- Present}
    \resumeItemListStart
        \resumeItem{Artistic QR code generator}{
            Made the 4th most used tool by the company with 30k+ uses that has landed branding deals and social media exposure. Led to being offered part time position for after internship.
        }
        \resumeItem{Improved Translations}{
            Deployed models for 20 extra dialects and 100 extra languages, transliteration, and glossary features to support expansion into regions like Senegal and improve products in India.
        }
        \resumeItem{Slack Bot}{
            Worked closely with partners like Zephyr to implement an automated tool to integrate custom Slack bots into Workspaces with custom data (Vector DBs), 200+ languages, and audio/video support.
        }
        \resumeItem{Python}{
            \underbar{MLOps}, \underbar{Kubernetes}, \underbar{Docker}, \underbar{Google Cloud Platform}, \underbar{Django}, and \underbar{ML APIs} e.g. OpenAI.
        }
    \resumeItemListEnd

    \resumeSubheading{Akvelon}{Software Development Intern}{Jun. 2023 -- Aug. 2023}
    \resumeItemListStart
        \resumeItem{Open source contributions}{
            to Microsoft Power BI across 2 visuals and 7 pull requests.
        }
        \resumeItem{Mentor's choice Leadership Award}{
            Led team of 4 to contribute to 5 visuals across ~20 pull requests.
        }
        \resumeItem{Applied contributions}{
            to analyze sensor data from a custom IOT device streaming data to the cloud.
        }
        \resumeItem{TypeScript/C++}{
            \underbar{Power BI Custom Visuals}, \underbar{Automated Testing}, \underbar{Embedded Systems}, and \underbar{Azure IOT Hub}.
        }
    \resumeItemListEnd
    \vspace{-10pt} % Hacky fix for awkward extra space that randomly appears

    \resumeSubheading{University of Washington ICTD Lab}{Undergraduate Researcher}{Sep. 2022 -- Present}
    \resumeItemListStart
        \resumeItem{eKichabi v2 Django Developer}{
            In charge of the backend for the eKichabi v2 project, a digital intervention to connect 10K farmers in Tanzania. Maintained and expanded the USSD server and Android app.
        }
        \resumeItem{Co-first authored eKichabi v2 paper}{
            Worked closely with Dr. Anderson (UW) and PhD student Raghunath (UW) to write a paper on scaling technological interventions -- submitted to ACM SIGCHI.
        }
        \resumeItem{Technological Consultant}{
            Maintenance, consulting and analyzing data for an economic impact analysis of eKichabi v2 by Dr. Anderson (UW), Dr. Dillon (Cornell), and Dr. Rudder (UChicago).
        }
        \resumeItem{Python/Java}{\underbar{Jupyter}, \underbar{Django}, \underbar{MySQL}, \underbar{Redis}, and \underbar{Android Studio}}.
    \resumeItemListEnd

    \resumeSubheading{Self Employed}{Private Tutor}{May. 2022 -- Present}
    \resumeItemListStart
        \resumeItem{Provided lessons for 10 students}{
            3rd-12th grade through a self-designed coding curriculum.
        }
        \resumeItem{Cascade Enrichment Tech Lead}{
            Developed K-12 Assessment Software, designed Remote Certification process, and trained/certified 20+ educators. \underbar{JavaScript}, and \underbar{Automation Software}.
        }
    \resumeItemListEnd

    \resumeSubheading{European Environment Agency}{Data Science Intern}{Apr. 202o -- May. 2022}
    \resumeItemListStart
        \resumeItem{3 Water Framework Directive Projects}{
            Biodiversity, Water-flow, and Horizon Scanning.
        }
        \resumeItem{Results used by the EEA and in 40 countries}{
            Data visualizations, model evaluations, literature review, reports, and presentations. \underbar{Python}, \underbar{Pandas}, \underbar{PySpark}, \underbar{Azure ML Studio}, \underbar{Azure Databricks}, and Excel.
        }
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
    \resumeTopItem
        {University of Washington}
        {Bachelor's in CS (3.86 GPA, 3.96 in CS)}
        {Sep. 2022 -- ca. 2025}{
            Design Build Fly Electric Engineer, UW Symphony Orchestra Violin 1
        }
    \resumeSubheading
        {Bothell High School}
        {Valedictorian (4.0 GPA)}
        {Aug. 2018 -- Jun. 2022}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
    \resumeTopItem{WiFi RSSI}{Windows App}{Jan. 2022 -- Feb 2022}{
        3700+ downloads, 4.4/5 rating. GUI to calculate the RSS in dBm of available networks by analyzing WiFi packets and BSSIDs. Made for WA Science Olympiad to standardize evaluation of antennas made for new WiFi Lab event.
    }
    \resumeTopItem{Attendance Scanner}{Web App}{Aug. 2022 -- Jun. 2023}{
        Attendance system with QR-code enhancements, a SQLite database, \underbar{Braintree} subscription system, and \underbar{OAuth2}. Used by SYSO (my old youth orchestras of $\sim 500$ people). Prototyped in 2 weeks, then turned into a commercial product in collaboration with Claire Li. \underbar{Firebase}, \underbar{Node.js}, \underbar{Express}, and \underbar{Web Components}.
    }
\resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
    \resumeLineItem{Languages}{JavaScript, TypeScript, Python, Java, C++, C\#, SQL}{6+ years}
    \resumeLineItem{Tech}{Google Cloud Platform, Payment APIs, React, OAuth2, MySQL, Docker, Unix, Git}{3+ years}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}